Evolution Reinforces Cooperation with the Emergence of Self-Recognition Mechanisms: an Empirical Study of strategies in the Moran process for the Iterated Prisoner's

### 2018-01-11 main.tex
Tweak the title.

% Title
\title{Evolution Reinforces Cooperation with the Emergence of Self-Recognition
       Mechanisms: Empirical Study of strategies in the Moran process for the
       Iterated Prisoner's}
\author[1]{Vincent Knight}
\author[2]{Marc Harper}
\author[1]{Nikoleta E. Glynatsi}
\author[3]{Owen Campbell}

>>>>

% Title
\title{Evolution Reinforces Cooperation with the Emergence of Self-Recognition
       Mechanisms: an Empirical Study of strategies in the Moran process for the
       Iterated Prisoner's}
\author[1]{Vincent Knight}
\author[2]{Marc Harper}
\author[1]{Nikoleta E. Glynatsi}
\author[3]{Owen Campbell}
